Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-11-01 paper/main.tex
Updated tahoe hashing example image

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.9\columnwidth]{Tahoe-hashing.pdf}
    \caption{Tahoe-LAFS: Hashing operations in mutable files.}
    \label{fig:tahoehashing}
    \emph{Figure from
     \href{http://tahoe-lafs.org/source/tahoe/trunk/docs/specifications/mut.svg}
     {tahoe-lafs.org}}
\end{figure}

>>>>

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.9\columnwidth]{Tahoe-hashes.pdf}
    \caption{Tahoe-LAFS: Example of hashing operations.}
    \label{fig:tahoehashing}
    \emph{Figure based on
     \href{http://tahoe-lafs.org/source/tahoe/trunk/docs/specifications/CHK-hashes.svg}
     {CHK-hashes.svg from tahoe-lafs.org}}
     %TODO: Footnote with full URL using footnotemark
\end{figure}
